R Tools for Obspack, Footprints and Receptors (rtorf)

### 2024-03-06 README.Rmd
rename robspack to rtorf
add actions

![GitHub commit
activity](https://img.shields.io/github/commit-activity/y/ibarraespinosa/rtorf)
[![R build
status](https://github.com/ibarraespinosa/rtorf/workflows/R-CMD-check/badge.svg)](https://github.com/ibarraespinosa/rtorf/actions)
[![R build
status](https://github.com/ibarraespinosa/rtorf/workflows/draft-pdf/badge.svg)](https://github.com/ibarraespinosa/rtorf/actions)

>>>>

![GitHub commit
activity](https://img.shields.io/github/commit-activity/y/ibarraespinosa/rtorf)

[![R build
status](https://github.com/ibarraespinosa/rtorf/workflows/draft-pdf/badge.svg)](https://github.com/ibarraespinosa/rtorf/actions)

[![R-CMD-check](https://github.com/ibarraespinosa/torf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ibarraespinosa/torf/actions/workflows/R-CMD-check.yaml)
